Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Rewrite section 2 intro

\section{Impact on Actions} \label{sec:ref_frame}
We first demonstrate the importance of measuring the Galactic midplane to very
high accuracy. We explore the consequence of an incorrect midplane in the
context of computing orbital actions of disk stars. An inaccuracy in the
midplane is only one potential systematic error in the way actions are
presently computed. The assumed axisymmetric model of the Galaxy may be a poor
description of the Galactic potential, and the parameters in this axisymmetric
model may be estimated incorrectly.

In this work, we assume both that an axisymmetric model of the Galaxy is a
good description of the potential and that we have correctly determined the
parameters of that model. We are only concerned with an inaccuracy

>>>>

\section{Impact on Actions} \label{sec:ref_frame}
We first demonstrate the importance of measuring the Galactic midplane and
Solar radius to very high accuracy. To be clear, the consequences we explore
here may also arise from various other observational errors. For instance, the
symmetrized Galactic potential used by observers may not be a good description
of the true potential --- or the parameters used may be incorrect. In this
Section, we assume these approximations are valid and simply explore the
consequences of an inaccurate Galactocentric coordinate system.
